A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-08-23 main.tex

\subsection{Attack Generation Time}
A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output. Assuming a uniform distribution, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
\begin{equation}
    T_a := t_a \cdot n \cdot i.
\end{equation}
In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}. 
\cm{
In reality, the attack time will not be drawn from a uniform distribution and prior research~\cite{meyers_aft} has shown that by treating model and attack parameters as  this can be more accurately approximated with $t_{a}'$
}
\begin{equation}
	t_{a}' \approx \mathbb{E}_{S_\theta}[T] =  \int_{0}^{t^*} S_{\theta}(t) dt.
\end{equation}

@@

\subsection{TRASH Score}
\cm{
With an estimate of the expected survival time in hand,  quantify the cost-normalized failure rate, or the ratio of training time to attack time. Assuming that the cost scales linearly -- as discussed above-- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a} \approx \mathbb{E}_{S\theta}[T]$). Using the definition of $\varepsilon$ from Equation~\ref{eq:adv_success}, we can express the cost of failure in adversarial terms as follows:
}
\begin{equation}
	\textrm{TRASH~Score}=\frac{t_t}{\mathbb{E}_{\theta}[T \,|\, 0 < \varepsilon \leq \varepsilon^*]} = \frac{t_t}{t_a'}.
	\label{eq:cost}
\end{equation}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth,clip]{plots/combined/acc.pdf}
    \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot. Each color is a different device and the datasets are displayed along the x-axis. Outliers are denoted with a white dot.}}
    \label{fig:acc}
\end{figure}

@@

The monetary cost for each dataset and each piece of hardware is shown in Figure~\ref{fig:cost}. For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample. In the best case scenario, they are comparable, but attacks consistently succeed with only 100 samples (Figure~\ref{fig:acc}) while model training requires orders of magnitude more. 
%  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_trash_score.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_trash_score.pdf}
        \caption{ }
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_trash_score.pdf}
        \caption{}
    \end{subfigure}
    \caption{\cm{TODO}}
    \label{fig:trash}
\end{figure*}
\subsection{AFT Models}
\label{res:aft}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}{\textwidth}
        \includegraphics[width=.8\textwidth]{plots/combined/weibull_aft.pdf}
    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \includegraphics[width=.8\textwidth]{plots/combined/log_normal_aft.pdf}
    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \includegraphics[width=.8\textwidth]{plots/combined/log_logistic_aft.pdf}
    \end{subfigure}
    \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
    \label{fig:aft}
\end{figure*}

>>>>

\subsection{Attack Generation Time}
A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output. Assuming a uniform distribution, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
\begin{equation}
    T_a := t_a \cdot n \cdot i.
    \label{eq:attack_time}
\end{equation}
In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}. 
\cm{
In reality, the attack time will not be drawn from a uniform distribution and prior research~\cite{meyers_aft} has shown that by treating model and attack parameters as  this can be more accurately approximated with $t_{a}'$
}
\begin{equation}
	t_{a}' \approx \mathbb{E}_{S_\theta}[T] =  \int_{0}^{t^*} S_{\theta}(t) dt.
 \label{eq:aft_time}
\end{equation}

@@

\subsection{TRASH Score}
\cm{
With an estimate of the expected survival time in hand,  quantify the cost-normalized failure rate, or the ratio of training time to attack time. Assuming that the cost scales linearly -- as discussed above-- the model builder's cost is proportional to the training time ($C_t \propto t_{t}$), and the attacker's cost is proportional to the attack time, which is approximately the expected survival time ($C_{a} \propto t_{a}' \approx \mathbb{E}_{S\theta}[T]$). Using the definition of $\varepsilon$ from Equation~\ref{eq:adv_success} and definition of $t_a'$ from Equation~\ref{eq:aft_time}, we can express the cost of failure in adversarial terms as follows:
}
\begin{equation}
	\textrm{TRASH~Score}=\frac{t_t}{\mathbb{E}_{\theta}[T \,|\, 0 < \varepsilon \leq \varepsilon^*]} = \frac{t_t}{t_a'}.
	\label{eq:cost}
\end{equation}

@@

@@

The monetary cost for each dataset and each piece of hardware is shown in Figure~\ref{fig:cost}. For all three datasets across all three pieces of hardware, the cost of training on a single sample often exceeds the cost of attacking a single sample. In the best case scenario, they are comparable, but attacks consistently succeed with only 100 samples (Figure~\ref{fig:acc}) while model training requires orders of magnitude more. 
%  However, we note that the attacker only needs to be lucky once, whereas the the model builder must be lucky always.
\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth,clip]{plots/combined/acc.pdf}
    \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot. Each color is a different device and the datasets are displayed along the x-axis. Outliers are denoted with a white dot.}}
    \label{fig:acc}
\end{figure}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}{\textwidth}
        \includegraphics[width=.8\textwidth]{plots/combined/weibull_aft.pdf}
    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \includegraphics[width=.8\textwidth]{plots/combined/log_normal_aft.pdf}
    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \includegraphics[width=.8\textwidth]{plots/combined/log_logistic_aft.pdf}
    \end{subfigure}
    \caption{Coefficients of the Covariates for the Weibull, Log-Normal, and Log-Logistic AFT models. Here, "Random State" is used as a control variable that should be (and is) close to 0. \cm{A positive value indicates that covariate increases the survival time and negative value indicates that covariate decreases the survival time. The symbols $T_i$ and $T_t$ refer training and inference time for all samples, while $\lambda$ refers to the benign accuracy (accuracy on the un-altered samples).}}
    \label{fig:aft}
\end{figure*}
\subsection{AFT Models}
\label{res:aft}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/weibull_trash_score.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_trash_score.pdf}
        \caption{ }
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_normal_trash_score.pdf}
        \caption{}
    \end{subfigure}
    \caption{\cm{TODO}}
    \label{fig:trash}
\end{figure*}
